Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-09-05 chatbot_classification/aaai_2021/paper.tex
version 1.   modified:   paper.tex   new file:   paper.ver01.pdf

  \begin{figure*}[t]
    \begin{centering}
      \includegraphics[scale=0.72]{picture/picture4} 
      \par
    \end{centering}
    \caption{
      \textbf{Network   Structure   of  joint  SFC:}  a  joint  model  of
      sentence-pair   model   and   text   classification   model  organized  in
      joint  structure by completing different tasks at different network
      layers.
    }
    \label{fig:framework}
  \end{figure*}

@@

          (task1 only) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          (task2 only) & & & & & & & & & & & & & & & & & & & &\tabularnewline

>>>>

  \begin{figure*}[t]
    \begin{centering}
      \includegraphics[scale=0.72]{picture/picture4} 
      \par
    \end{centering}
    \caption{
      \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
      the  same  network  from  stage  1  and  stage 2, with the only difference
      whether two stages being jointly trained.
    }
    \label{fig:framework}
  \end{figure*}

@@

          (task1) & & & & & & & & & & & & & & & & & & & &\tabularnewline

@@

          (task2) & & & & & & & & & & & & & & & & & & & &\tabularnewline
